2. Simulated Data

### 2021-07-30 analysis/reports/rmd/02_dataProcessing.Rmd
post data collection

```{r readData}
# read replication data
DT <- read.csv(paste("../..", recentCSV, sep = "/"), 
               stringsAsFactors = FALSE) %>%
  data.table()

@@

@@

>>>>

```{r readAll}

# DT <- read.csv("../../../data/simulation/all_apps_wide.csv",
#                stringsAsFactors = FALSE) %>% data.table()

files <- list.files(path = "../../../data/replication/",
                       recursive = TRUE,
                       full.names = TRUE)
csvs <- list()

for(i in files){
  name <- str_extract(string = i,
                      pattern = "2021.*")

  temp <- read.csv(i, 
                   stringsAsFactors = FALSE) %>%
    data.table()

  csvs[[name]] <- temp
}

full <- rbindlist(l = csvs,
                  use.names = TRUE) %>%
  data.table()

DT <- full[participant._index_in_pages > 2 & 
             participant.time_started != "" & 
             participant.label != "" &
             !(is.na(dPGG.1.player.contribution))]

rm(list = c("files", "temp", "full"))
```

```{r readData, eval = FALSE}
# read replication data
DT <- read.csv(paste("../..", recentCSV, sep = "/"), 
               stringsAsFactors = FALSE) %>%
  data.table()

@@

Unfortunately, I made a mistake calculating the ```share```. For this reason, it will be recalculated here:

```{r recalcShare}
replication[, share := contribution/endowment]
```

@@

```{r}
replication[,
            .(contribution = mean(contribution),
              endowment = mean(endowment),
              share = mean(contribution/endowment),
              share2 = mean(share)),
            by = c("round")]
```
